Hierarchical ARIMA

### 2020-08-25 KB_modeling.Rmd
model updates

playoff_success <- read.csv("MLB_Postseason_Success.csv", stringsAsFactors = FALSE) %>%
  mutate_all(na_if,"") %>%
  replace(is.na(.), "No Playoffs")

#combining new palyoff dataset with dat
dat <- left_join(dat, playoff_success, by = c("team", "year")) %>%
  select(-c(DivWin, WCWin, LgWin, WSWin)) # deselecting unnecessary variables

dat <- dat %>%
  # mutate_at(vars(DivWin, WCWin, LgWin, WSWin), funs(as.logical)) %>%
  mutate(
  #   playoffs = case_when(
  #     WSWin ~ "Won WS",
  #     LgWin ~ "Lost WS",
  #     WCWin  ~ "Won Wild Card",
  #     DivWin  ~ "Won Division",
  #     TRUE ~ "No Playoffs"
  #   ),
    playoffs = forcats::fct_inorder(playoffs), # not exactly sure what this line of code does? do we still need?
    phase = case_when(
      month < 04 | month > 10 ~ "Summer",
      month == 04 ~ "Opening",
      month < 10 & month > 04 ~ "Season",
      month == 10 ~ "Playoffs"
    ),
    phase = forcats::fct_reorder(phase, month), # not exactly sure what this line of code does? do we still need?
    is_playoffs = as.integer(phase == "Playoffs")
  ) %>%
  mutate_at(vars(month, year, team), funs(factor))

summary(dat$playoffs)
```

>>>>

playoff_success <- read_csv("MLB_Postseason_Success.csv") %>%
  mutate_all(na_if,"") %>%
  replace(is.na(.), "No Playoffs")

#combining new palyoff dataset with dat
dat <- dat %>% 
  left_join(playoff_success, by = c("team", "year"))

dat <- dat %>%
  select(-c(DivWin, WCWin, LgWin, WSWin)) %>%
  mutate(
  #   playoffs = case_when(
  #     WSWin ~ "Won WS",
  #     LgWin ~ "Lost WS",
  #     WCWin  ~ "Won Wild Card",
  #     DivWin  ~ "Won Division",
  #     TRUE ~ "No Playoffs"
  #   ),
    playoffs = forcats::fct_inorder(playoffs), # not exactly sure what this line of code does? do we still need?
    phase = case_when(
      month < 04 | month > 10 ~ "Off-Season",
      month == 04 ~ "Opening",
      month < 10 & month > 04 ~ "Season",
      month == 10 ~ "Playoffs"
    ),
    phase = forcats::fct_reorder(phase, month), # not exactly sure what this line of code does? do we still need?
    is_playoffs = as.integer(phase == "Playoffs")
  ) %>%
  mutate_at(vars(month, year, team), funs(factor))

summary(dat$playoffs)

dat %>%
  write_csv("MLB_combined.csv")
```
